---
title: "Monash EBS xaringan Template"
subtitle: ""
author: "Your Name"
date: "`r Sys.Date()`"
seal: false
output:
  xaringan::moon_reader:
    css: "monashEBS.css"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

## Slides with bullets

- Bullet 1
- Bullet 2
- Bullet 3

Use `</span>` to <span style="color:chocolate">highlight</span> some text

### Some enumeration

1. The first item
1. Stuff
1. Nonsense

---
## Build incremental slides

Use two dashes -- to separate content on a slide.
--

- Bullet 1
--

- Bullet 2
--

- Bullet 3


---
class: inverse, center, middle

# Using R

---
## Slide with R output

```{r cars, echo = TRUE}
summary(cars)
```

---

## Slide with graphics

```{r pressure, fig.align='center', out.width = "60%"}
plot(pressure)
```

---
## Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;
2. There should not be spaces after the opening `$` or before the closing `$`.
3. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---
## Slide with mathematics

Quantile score for observation $y$. For $0<p<1$:

$$S(y_t,q_t(p))=\;\begin{cases}p(y_t-q_t(p)),& \text{if} \quad y_t \ge q_t(p)\\(1-p)(q_t(p)-y_t),& \text{if} \quad y_t < q_t(p).\end{cases}$$



Average score over all percentiles gives the best distribution forecast:

$QS = \frac{1}{99T}\sum_{p=1}^{99}\sum_{t=1}^T S(q_t(p),y_t)$

To center, use  `$$`

$$QS = \frac{1}{99T}\sum_{p=1}^{99}\sum_{t=1}^T S(q_t(p),y_t)$$
---
class: inverse, center, middle

#  RMarkdown Examples

---
## R Figure

The following code generates the plot on the next slide (taken from
`help(bxp)` and modified slightly):


```{r pressureCode, eval=FALSE, echo=TRUE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "orange",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```

---
## R Figure

```{r pressureFig, echo=FALSE, fig.align='center', out.width = "60%"}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "orange",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```
---
class: inverse

## R Figure


```{r pressureCode2, eval=TRUE, echo=TRUE, out.width = "40%", fig.align='center'}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "orange",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```

---
## R Table

A simple `knitr::kable` example:


```{r }
knitr::kable(mtcars[1:4, 1:7],caption="(Parts of) the mtcars dataset",  
             format = 'html')
```

---
## Resources

- overview


- two column


- gif


- gganimation


- ggplot


- R stopwatch


- full image


- link

---


class: center, middle

# Thanks!

